---
title: ""
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(kableExtra)
```

<style>
  .abstract { padding-top: 1em; display: none; }
</style>

<br><br>
Methods & Metascience is a working group at the Institute of Neuroscience and Psychology at the University of Glasgow. You can find our schedule and materials at this website.

Our regular meetings are Wednesday afternoons from 2pm-3pm in 605 (aka Meeting room) or 529/551 at 62 Hillhead St (aka "Seminar" room) or Room 520 (Computer Lab) in the Boyd Orr. In addition to talks, we also run training events. If you would like to present or run a training workshop, please let [Dale](mailto://dale.barr@glasgow.ac.uk) know!

For an up-to-date list of talks, please see [the events list](http://www.psy.gla.ac.uk/events/index.php?sub=12).

### Schedule

```{r, results='asis'}

rss <- readLines("https://samoa.dcs.gla.ac.uk/events/rest/Feed/rss/141")

schedule <- tibble::tribble(
  ~Date, ~Speaker, ~speaker_link, ~Title, ~Time, ~Room, ~Abstract,
  "2018-10-03", "Christoph Schild", "https://twitter.com/schildchristoph", 
    "Introduction to the [formr](https://formr.org/) survey framework in R [(slides)](https://osf.io/gu23h/)", 
    "15:00-16:00", "Seminar Room 529/551", "",

  "2018-10-10", "Dale Barr", "https://twitter.com/dalejbarr", 
    "Mixed-effects modeling of temporal autocorrelation: Keep it minimal",
    "14:00-15:00", "Meeting Room 605", "",

  "2018-10-24", "Ben Jones", "https://twitter.com/Ben_C_J",
    "Writing Registered Reports [(slides)](slides/2018_10_24_Ben_Jones.pdf)",
    "14:00-15:00", "Seminar Room 529/551", "",

  "2018-10-31", "Lisa DeBruine", "https://twitter.com/lisadebruine",
    "Your First Shiny App [(tutorial)](https://psyteachr.github.io/shiny-tutorials/01-first-app.html)",
    "14:00-15:00", "Boyd Orr Computer Lab Room 520", "",

  "2018-11-07", "Jessica Flake", "https://www.jessicakayflake.com/", 
    "The Fundamental Role of Construct Validity in Original and Replicated Research",
    "14:00-15:30", "Seminar Room 529/551", "",

    "2018-11-14", "Martin Lages", "https://www.gla.ac.uk/schools/psychology/staff/martinlages/#/",
    "Spot the celebrity lookalike!",
    "14:00-15:00", "Meeting Room 605", "",

  "2018-11-21", "Robin Ince", "http://www.robinince.net/", 
    "The Problem of Multiple Comparisons in Neuroimaging",
    "14:00-15:00", "Meeting Room 605", "",
  
  "2018-11-28", "Larry Barsalou", "http://barsaloulab.org/",
    "The Situated Assessment Method (SAM^2): A new approach to measuring, understanding, and predicting health behaviours",
    "14:00-15:00", "Meeting Room 605", "",
  
  "2018-12-05", "Jack Taylor", "https://github.com/Jack-Tay",
    "LexOPS: A Web App for Stimulus Generation in Psycholinguistics ([github](https://github.com/Jack-Tay/LexOPS))",
    "14:00-15:00", "Meeting Room 605", "",
  
  "2018-12-12", "Dale Barr", "https://twitter.com/dalejbarr",
    "Randomizing and automating assessment with the [R exams](http://www.r-exams.org) package [(slides)](slides/r-exams.pdf)",
    "13:00-14:00", "Meeting Room 605", 
  "I will give an overview of the open source \"exams\" package for R, which assists in the generation and assessment of electronic and written exams. I recently used this package for the first time to create a written exam for my L3 statistics course. We validated the performance of the automatic scanning of answers and found above 99% accuracy. Although it requires substantial time to set up, over the long run, the exams package makes creating and marking exams more efficient. More information about the package can be found at http://www.r-exams.org.",

  "2019-02-06", "Lisa DeBruine", "https://twitter.com/lisadebruine",
    "Discussion prep for Friday seminar (by Daniël Lakens)<br>Readings: [Equivalence Testing for Psychological Research](https://doi.org/10.1177/2515245918770963) & [Justify Your Alpha](https://psyarxiv.com/9s3y6/) (+[related blog post](http://daniellakens.blogspot.com/2018/12/testing-whether-observed-data-should.html))",
    "14:00-15:00", "Meeting Room 605", "",
  
  "2019-02-08", "Daniël Lakens", "https://twitter.com/lakens",
    "Justify Everything ([slides](https://osf.io/j4s3c/))",
    "15:30-16:30", "Seminar Room 529/551", "",
  
  "2019-03-27", "Anna Henschel", "https://twitter.com/AnnaHenschel", 
  "Adventures with rtweet and tidytext", 
  "14:00-15:00", "Seminar Room 529/551", 
  "We have always suspected it: Twitter and #rstats go hand in hand. In this tutorial we will do some web-scraping with the rtweet package and look at various fun ways to analyse this data taking advantage of the tidytext package. Join this tutorial if, for example, you want to learn how to make a colourful word cloud out of everything you ever tweeted or if you want to plot what people have been saying about the Great British Bake Off over time.",
  
  "2019-04-10", "Robin Ince", "http://www.robinince.net/", 
  "A gentle introduction to the Partial Information Decomposition", 
  "14:00-15:00", "Seminar Room 529/551", 
  "In many cases in neuroimaging or data analysis we evaluate a statistical dependence in many variables, and find effects in more than one. For example, we might find an effect between a presented stimulus and neural responses in different spatial regions, time periods or frequency bands. A natural question in such situations is to what extent is the statistical relationship in the two responses common, or overlapping, and to what extent is there a unique effect in one response that is not related to the other response. An information theoretic framework called the Partial Information Decomposition (PID) has been proposed to address these questions. The first part of the session will be a gentle introduction to information theoretic quantification of statistical interactions, introducing co-information, redundancy, synergy and the basic theory of the PID, as well as introducing some applications (including, interactions between neural responses, interactions between multi-modal stimulus features in speech, interactions between neural responses and behaviour and predictive model comparison). The second part of the session will go into a bit more detail into the details of the implementation of the PID including the theory and computation of the Iccs redundancy measure, and more discussion of issues such a misinformation (negative unique information), applications etc. There will be a break between the two parts to give people the chance to opt-out of the more technical second part.",
  
  "2019-04-23", "Martin Lages", "", 
  "Variance Constraints for Hierarchical Signal Detection Models", 
  "14:00-15:00", "Seminar Room 529/551", 
  "Bayesian models typically place uninformative or weakly informative priors on parameters. Using a well-known data set on inductive and deductive reasoning, it is illustrated how incorporating variance constraints can help to estimate critical parameters and compare signal detection models with equal and unequal variance.",
  
  "2019-05-01", "Maria Gardani & Satu Baylan", "", 
  "Systematic reviews and meta analysis", 
  "14:00-15:00", "Seminar Room 529/551", "",

  "2019-06-12", "Christoph Scheepers and Dale Barr", "https://www.gla.ac.uk/researchinstitutes/neurosciencepsychology/staff/christophscheepers/",
    "Mixed-Effects Models Q&A [(Christoph's materials on ordinal logistic regression)](slides/Scheepers_Ordinal_Slides_and_Data.zip)",
    "14:00-15:00", "Seminar Room 529/511", 
  "If you have questions about mixed-effects modeling, here is an opportunity to come and ask! Dale and Christoph will be there to field your questions.",
  
  "2019-09-24", "Jack Taylor and Lisa DeBruine", "https://twitter.com/JackEdTaylor",
  "R Shiny Afternoon ([tutorial](https://psyteachr.github.io/shiny-tutorials/))", 
  "13:00-17:00", "Seminar Room 529/511", 
  "Shiny is an R package that makes it easy to create interactive apps in R that can be deployed to the web (find out more here: https://shiny.rstudio.com/). Shiny apps are great for teaching concepts, presenting research results, and automating simple tasks. This four-hour workshop (1pm to 5pm) will cover: - A basic introduction to Shiny - How to collect data from participants in Shiny (e.g. questionnaires) - How to build user-friendly apps for solving specific problems Please bring your own laptop, and come having already installed R, RStudio, and the Shiny package.",
  
  "2019-10-02", "Carolyn Saund", "http://carolynsaund.me/",
  "Crowdsourcing: The Good, The Bad, and The Ugly ([slides](https://github.com/csaund/presentations/blob/master/crowdsourcing_pres.pdf))",
  "14:00-15:00", "Seminar Room 529/511", "An introduction to crowdsourcing methods for online surveys and experiments. First, a brief introduction to crowdsourced data for the skeptics: history, ethics, stats on data reliability, designing tasks, what should and should not be done via the magic of the internet. Rife with warnings, caveats, and cautionary tales. Secondly, a hands-on, step-by-step introductory demo of designing and deploying tasks for online workers. Not a workshop, just a demo, so no need to bring laptops. Will your fears be assuaged, or validated? You'll have to come to find out!",
  
  "2019-10-09", "Benedict Jones", "https://twitter.com/Ben_C_J",
  "Introducing p curve ([slides](https://osf.io/d3zea/))", 
  "14:00-15:00", "Seminar Room 529/511", 
  "P-curve is an alternative to traditional forms of meta-analysis that, in principle, allows you tell whether or not a published literature contains evidentiary value. This short session will (1) introduce the method by using a preregistered case study from the face perception literature and (2) discuss the advantages and disadvantages of the p-curve method.",
  
  "2019-10-18", "Anne Scheel", "https://www.tue.nl/en/our-university/departments/industrial-engineering-innovation-sciences/the-department/staff/detail/ep/e/d/ep-uid/20176208/",
  "Is Hypothesis Testing Overused in Psychology?",
  "12:00-13:00", "Seminar Room 529/511", 
  "A central goal of many of the open-science reforms proposed in reaction to the replication crisis is to reduce false-positive results in the literature. Very often, they assume that research consists of confirmatory hypothesis tests and that 'questionable research practices' are ways in which researchers cut corners to present evidence in favour of hypotheses that may in fact be false. Two increasingly popular methods to prevent this from happening are preregistration and Registered Reports: Both require that authors state their hypotheses and analysis plan before conducting their study, which is supposed to prevent twisting the data to fit the narrative (e.g. p-hacking) or twisting the narrative to fit the data (hypothesising after results are known). In theory, this practice safeguards the validity of inferences drawn from hypothesis tests by removing any 'wiggle room' authors could exploit to produce spurious positive results. In practice, many psychologists seem to struggle to fit their research into this revised, now much more narrow framework of confirmatory hypothesis testing: Preregistration has been accused of stifling creativity, is described as difficult even by its proponents, and analyses of published preregistrations show that most do not sufficiently restrict the above-mentioned wiggle room. I want to argue that by making the very strict requirements of a confirmatory hypothesis test so explicit, preregistration and Registered Reports reveal that hypothesis testing may be the wrong tool for a substantial number of research questions in psychology. The conflation of exploratory and confirmatory research that psychologists have been used to may have stifled the development of a framework for high-quality exploratory research, which is the necessary basis for developing hypotheses in the first place. As such, resistance against preregistration and some of the growing pains the format is experiencing may simply be a consequence of it laying bare the misfit between research goals and the excessive focus on hypothesis testing in psychology. If this is true, psychologists may be well advised to shift this focus and work towards better literacy in the exploratory ground work that precedes confirmatory hypothesis tests.",
  
  "2019-10-22", "Jo Neary and Kathryn Machray", "https://twitter.com/joanne_neary",
  "Take a picture, it'll last longer: Practical and ethical considerations on using visual methods in qualitative research",
  "14:00-15:00", "Seminar Room 529/511", 
  "For many people, taking and sharing photographs is an everyday behaviour, and is a way of sharing parts of your life (and your identity) with friends and family. This session discusses how research can utilise this everyday practice in a research setting, in order to shine a light on the elements of a participants’ life that may be inaccessible to traditional methods (such as surveys). In doing so, we explore the links between visual methods and ethnography, the use of visual methods in readdressing the power imbalance inherent in research, and some of the practical and ethical considerations of the method. This session will include two case studies from our research (children’s experience of neighbourhood demolition; men’s experience of food poverty), as well as participation from the audience.",
  
  "2019-10-29", "Andrew Burns", "https://www.gla.ac.uk/schools/socialpolitical/research/students/andrewburns/", 
  "Qualitative data – reaching the parts that statistics can’t?",
  "12:00-13:00", "Seminar Room 529/511", 
  "An interactive seminar using data collected in an ethnography of homelessness (using participant observation, observation, and qualitative [walking] interviews). While originally used for an anthropological analysis, we can use this seminar to explore the place of such data in psychology (is there a place?) including the methods of data collection, different approaches to coding/analysis, writing up, and the reflexive researcher.",
  
  "2019-11-13", "Dale Barr", "https://twitter.com/dalejbarr",
  "Containerize your code: Creating reproducible software environments [(slides)](barr_container/index.html)",
  "14:00-15:00", "Seminar Room 529/511", "",

  "2020-01-08", "Discussion of Yarkoni (2019)", "",
  "Is there a generalizability crisis in psychology and neuroscience? [paper](https://psyarxiv.com/jqw35)",
  "14:00-15:00", "Seminar Room 529/511", "",

  "2020-01-15", "Guillaume Rousselet", "https://twitter.com/robustgar",
  "Why interactions are difficult to interpret and many are simply uninterpretable ([slides](slides/rousselet_interactions.pdf))",
  "14:00-15:00", "Seminar Room 529/511", "",
  
  "2020-01-22", "Zoltan Dienes", "http://www.lifesci.sussex.ac.uk/home/Zoltan_Dienes/",
  "How to obtain evidence for the null hypothesis [paper](https://doi.org/10.1177/2515245919876960)", 
  "14:00-15:00", "Seminar Room 529/511", "To get evidence for or against one's theory relative to the null hypothesis, one needs to know what it predicts. The amount of evidence can then be quantified by a Bayes factor. It is only when one has reasons for specifying a scale of effect that the level of evidence can be specified for no effect (that is, non-significance is not a reason for saying there is no effect). In almost all papers I read people declare absence of an effect while having no rational grounds for doing so. So we need to specify what scale of effect our theory predicts. Specifying what one's theory predicts may not come naturally, but I show some ways of thinking about the problem. I think our science will be better for it!",

  "2020-01-28", "Lisa DeBruine", "https://twitter.com/LisaDeBruine",
  "R Workshop, part 1: Introduction to Data Simulation [(materials)](https://osf.io/xpskm/)",
  "13:00-14:30", "Boyd Orr 603", "",

  "2020-02-05", "Lisa DeBruine", "https://twitter.com/LisaDeBruine",
  "R Workshop, part 2: Understanding Mixed-Effects Models Through Data Simulation [(materials)](https://osf.io/xpskm/)",
  "13:00-14:30", "Boyd Orr 603", "",
  
  "2020-02-19", "Ruud Hortensius", "https://twitter.com/RuudHortensius",
  "Tools for Reproducible fMRI Analysis [(materials)](https://osf.io/c28jq/) [(slides PDF)](slides/hortensius_fMRI_tools.pdf)",
  "14:00-15:00", "Seminar Room 529/511", "On our way to transparent and reproducible neuroimaging we need to consider data and code in combination with the publication. In this talk, I will introduce a series of tools that the field has developed (BIDS, Heudiconv, MRIQC, MRIQCeption, fMRIprep, OpenNeuro, NeuroVault) that will not only help to achieve this goal of fully reproducible neuroimaging but also make a neuroimagers life easier. Note: while the tools are focussed on neuroimaging the principle holds for behavioural, eye-tracking and physiological measures (e.g., BIDS is applicable to these measures).",
  
  "2020-02-28", "Jessie Sun", "https://about.me/jessiesun",
  "Eavesdropping On Everyday Life",
  "12:00-13:00", "Seminar Room 529/511",
  "This talk considers the unique insights that can be gained by combining multiple methods for studying daily life. In the Personality and Interpersonal Roles Study (PAIRS), 300 participants completed experience sampling method (ESM) self-reports while wearing the Electronically Activated Recorder (EAR), an unobtrusive audio recording device, for one week. Over the past five years, nearly 300 research assistants have transcribed and coded participants’ behaviors and environments from over 300,000 EAR audio files. To provide two examples of questions that can only be answered by capturing actual behavior alongside ESM self-reports, I will describe two projects that have resulted from this dataset: 1) Do people have self-knowledge of their momentary personality states, and 2) What are people doing when they miss experience sampling reports? I will conclude by discussing the opportunities and challenges of implementing open practices with this highly-identifiable and repeatedly-used dataset.",
  
  "2020-04-29", "Lisa Kidd", "",
  "The X factor: Using Q-methodology to understand perspectives of supported self-management in stroke",
  "14:00-15:00", "Seminar Room 529/511", "",
  
  "2020-05-20", "Mine Çetinkaya-Rundel", "http://mine-cr.com/",
  "The art and science of teaching data science", 
  "12:00-13:00", "Seminar Room 529/511",
  "Modern statistics is fundamentally a computational discipline, but too often this fact is not reflected in our statistics curricula. With the rise of data science it has become increasingly clear that students want, expect, and need explicit training in this area of the discipline. Additionally, recent curricular guidelines clearly state that working with data requires extensive computing skills and that statistics students should be fluent in accessing, manipulating, analyzing, and modeling with professional statistical analysis software. In this talk, we introduce the design philosophy behind an introductory data science course, discuss in progress and future research on student learning as well as new directions in assessment and tooling as we scale up the course."
)


schedule %>%
  mutate(Speaker = ifelse(speaker_link == "", Speaker, paste0("[", Speaker, "](", speaker_link,")"))) %>%
  mutate(Abstract = ifelse(Abstract == "", "", paste0(" <a>abstract</a><p class='abstract'>",Abstract, "</p>"))) %>%
  mutate(Title = paste0(Title, Abstract)) %>%
  select(-Abstract) %>%
  select(-speaker_link) %>%
  arrange(rev(Date)) %>%
  kable(escape = FALSE) %>%
  kable_styling("striped")

```


<script>
  /* set up abstract toggling */
  $(document).ready(function () {
    $("a:contains(abstract)").click(function(e) {
      $(this).next().toggle();
      return false;
    });
  });
</script>
