---
title: ""
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```

<br><br>
Methodology & Metascience is a working group at the Institute of Neuroscience and Psychology at the University of Glasgow. You can find our schedule and materials at this website.

Our regular meetings are Wednesday afternoons from 2pm-3pm in 605 (aka Meeting room) or 529/551 at 62 Hillhead St (aka "Seminar" room) or Room 520 (Computer Lab) in the Boyd Orr. In addition to talks, we also run training events. If you would like to present or run a training workshop, please let [Dale](mailto://dale.barr@glasgow.ac.uk) know!

For an up to date list of talks, please see [the events list](http://www.psy.gla.ac.uk/events/index.php?sub=12).

### Schedule

```{r, results='asis'}

rss <- readLines("https://samoa.dcs.gla.ac.uk/events/rest/Feed/rss/141")

schedule <- tibble::tribble(
  ~Date, ~Speaker, ~speaker_link, ~Title, ~Time, ~Room,
  "2018-10-03", "Christoph Schild", "https://twitter.com/schildchristoph", 
    "Introduction to the [formr](https://formr.org/) survey framework in R [(slides)](https://osf.io/gu23h/)", 
    "15:00-16:00", "Seminar Room 529/551",

  "2018-10-10", "Dale Barr", "https://twitter.com/dalejbarr", 
    "Mixed-effects modeling of temporal autocorrelation: Keep it minimal",
    "14:00-15:00", "Meeting Room 605",

  "2018-10-24", "Ben Jones", "https://twitter.com/Ben_C_J",
    "Writing Registered Reports [(slides)](slides/2018_10_24_Ben_Jones.pdf)",
    "14:00-15:00", "Seminar Room 529/551",

  "2018-10-31", "Lisa DeBruine", "https://twitter.com/lisadebruine",
    "Your First Shiny App [(tutorial)](https://debruine.github.io/shiny-tutorials/)",
    "14:00-15:00", "Boyd Orr Computer Lab Room 520",

  "2018-11-07", "Jessica Flake", "https://www.jessicakayflake.com/", 
    "The Fundamental Role of Construct Validity in Original and Replicated Research",
    "14:00-15:30", "Seminar Room 529/551",

    "2018-11-14", "Martin Lages", "https://www.gla.ac.uk/schools/psychology/staff/martinlages/#/",
    "Spot the celebrity lookalike!",
    "14:00-15:00", "Meeting Room 605",

  "2018-11-21", "Robin Ince", "http://www.robinince.net/", 
    "The Problem of Multiple Comparisons in Neuroimaging",
    "14:00-15:00", "Meeting Room 605",
  
  "2018-11-28", "Larry Barsalou", "http://barsaloulab.org/",
    "The Situated Assessment Method (SAM^2): A new approach to measuring, understanding, and predicting health behaviours",
    "14:00-15:00", "Meeting Room 605",
  
  "2018-12-05", "Jack Taylor", "https://github.com/Jack-Tay",
    "[LexOPS](https://github.com/Jack-Tay/LexOPS): A Web App for Stimulus Generation in Psycholinguistics",
    "14:00-15:00", "Meeting Room 605",
  
  "2018-12-12", "Dale Barr", "https://twitter.com/dalejbarr",
    "Randomizing and automating assessment with the [R exams](http://www.r-exams.org) package [(slides)](slides/r-exams.pdf)",
    "13:00-14:00", "Meeting Room 605",
  
  "2019-02-06", "Lisa DeBruine", "https://twitter.com/lisadebruine",
    "Discussion prep for Friday seminar (by Daniël Lakens)<br>Readings: [Equivalence Testing for Psychological Research](https://doi.org/10.1177/2515245918770963) & [Justify Your Alpha](https://psyarxiv.com/9s3y6/) (+[related blog post](http://daniellakens.blogspot.com/2018/12/testing-whether-observed-data-should.html))",
    "14:00-15:00", "Meeting Room 605",
  
  "2019-02-08", "Daniël Lakens", "https://twitter.com/lakens",
    "Justify Everything (title TBA)",
    "15:30-16:30", "Seminar Room 529/551",

  "2019-06-12", "Christoph Scheepers and Dale Barr", "",
    "Mixed-Effects Models Q&A [(Christoph's materials on ordinal logistic regression)](slides/Scheepers_Ordinal_Slides_and_Data.zip)",
    "14:00-15:00", "Seminar Room 529/511"
)

schedule %>%
  mutate(Speaker = paste0("[", Speaker, "](", speaker_link,")")) %>%
  select(-speaker_link) %>%
  knitr::kable()

```

