---
title: "Methods & Meta-Science"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(jsonlite)
library(kableExtra)
library(tidyverse)

# load in current list
url <- "https://samoa.dcs.gla.ac.uk/events/rest/Event/getgroupevents/141?includeChildren=false&startDate=2018-01-01T00%3A00%3A00.000Z"
j <- read_json(url)

url2 <- "https://samoa.dcs.gla.ac.uk/events/rest/Event/getgroupevents/169?includeChildren=false&startDate=2018-01-01T00%3A00%3A00.000Z"
j2 <- read_json(url2)

j <- c(j, j2)

# map to a data frame
jdf <- purrr::map_df(j, function(x) {
  list(
    id = x$id,
    title = x$title,
    speaker_name = x$speaker,
    speaker_affiliation = x$speakerAffiliation,
    speaker_url = x$speakerUrl,
    abstract = x$description,
    start = x$startTime,
    end = x$endTime,
    Location = x$location$location,
    resources = ""
  )
})

```

```{r}
# add resources

jdf <- mutate(jdf, resources = case_when(
  id == 15409 ~ "[formr](https://formr.org/), [(slides)](https://osf.io/gu23h/)",
  id == 15450 ~ "[(slides)](/mms/slides/2018_10_24_Ben_Jones.pdf)",
  id == 15451 ~ "[(tutorial)](https://psyteachr.github.io/shiny-tutorials/01-first-app.html)",
  id == 15492 ~ "[LexOPS github](https://github.com/Jack-Tay/LexOPS)",
  id == 15562 ~ "[R exams](http://www.r-exams.org), [(slides)](/mms/slides/r-exams.pdf)",
  id == 15611 ~ "[Equivalence Testing for Psychological Research](https://doi.org/10.1177/2515245918770963), [Justify Your Alpha](https://psyarxiv.com/9s3y6/), [related blog post](http://daniellakens.blogspot.com/2018/12/testing-whether-observed-data-should.html)",
  id == 16267 ~ "[(slides)](https://osf.io/d3zea/)",
  id == 16547 ~ "[(slides)](/mms/barr_container/index.html)",
  id == 16659 ~ "[(slides)](/mms/slides/rousselet-interactions.pdf)",
  id == 16758 ~ "[(materials)](https://osf.io/xpskm/)",
  id == 16759 ~ "[(materials)](https://osf.io/xpskm/)",
  id == 16403 ~ "[(paper)](https://doi.org/10.1177/2515245919876960)",
  id == 17134 ~ "[(slides)](/mms/slides/hyllested_generalizability_theory.pdf)",
  id == 17130L ~ "[(slides)](/mms/slides/taylor-estimating-distributional-parameters.pdf)",
  TRUE ~ resources
))

```

```{r}
# delete cancelled talks
jdf <- filter(jdf, !id %in% c(16379L, 16229L, 15603L, 16746L, 16963L, 16933L))

# add missing 

jdf <- add_row(jdf,
               speaker_name = "Daniël Lakens", 
               speaker_url = "https://twitter.com/lakens", 
               speaker_affiliation = "Eindhoven University of Technology",
               title = "Justify Everything (Or: Why All Norms You Rely on When Doing Research Are Wrong)", 
               resources = "[(slides)](https://osf.io/j4s3c/)",
               start = "2019-02-08T15:30", 
               end = "2019-02-08T16:30", 
               Location = "62 Hillhead Street, Level 5, Seminar Room",
               abstract = "Science is difficult. To do good science researchers need to know about philosophy of science, learn how to develop theories, become experts in experimental design, study measurement theory, understand the statistics they require to analyze their data, and clearly communicate their results. My personal goal is to become good enough in all these areas such that I will be able to complete a single flawless experiment, just before I retire – but I expect to fail. In the meantime, I often need to rely on social norms when I make choices as I perform research. From the way I phrase my research question, to how I determine the sample size for a study, or my decision for a one or two-sided test, my justifications are typically ‘this is how we do it’. If you ask me ‘why’ I often don’t know the answer. In this talk I will explain that, regrettably, almost all the norms we rely on are wrong. I will provide some suggestions for attempts to justify aspects of the research cycle that I am somewhat knowledgeable in, mainly in the area of statistics and experimental design. I will discuss the (im)possibility of individually accumulating sufficient knowledge to actually be able to justify all important decisions in the research you do, and make some tentative predictions that in half a century most scientific disciplines will have become massively more collaborative, with a stronger task division between scholars working on joint projects.")

```


```{r, eval = FALSE}
# check for speakers with no url
filter(jdf, speaker_url == "") %>%
  select(speaker_name)

# check for speakers with no affiliation
filter(jdf, speaker_affiliation == "") %>%
  select(speaker_name)

## 17054, 17080, 17102
```


```{r}
# fixes for missing info

glasgow_speakers <- c("Lisa DeBruine", "Dale Barr", "Ben Jones", "Benedict Jones", "Guillaume Rousselet", "Martin Lages", "Robin Ince and Guillaume Rousselet", "Maria Gardani & Satu Baylan", "Jack Taylor and Lisa DeBruine", "Dr. Jo Neary & Kathryn Machray", "Lawrence Barsalou", "Jack Taylor", "Carolyn Saund", "Robin Ince", "Anna Henschel", "Ruud Hortensius")


## add speaker URLs
jdf <- mutate(jdf, speaker_url = case_when(
  speaker_name == "Lisa DeBruine" ~ "https://debruine.github.io",
  speaker_name == "Dale Barr" ~ "https://twitter.com/dalejbarr/",
  speaker_name == "Robin Ince" ~ "http://www.robinince.net",
  speaker_name == "Carolyn Saund" ~ "http://carolynsaund.me/",
  speaker_name == "Jack Taylor" ~ "https://twitter.com/jackedtaylor",
  speaker_name == "Lawrence Barsalou" ~ "http://barsaloulab.org",
  speaker_name == "Ben Jones" ~ "https://twitter.com/Ben_C_J",
  speaker_name == "Benedict Jones" ~ "https://twitter.com/Ben_C_J",
  speaker_name == "Christoph Schild" ~ "https://twitter.com/schildchristoph",
  speaker_name == "Martin Lages" ~ "https://www.gla.ac.uk/schools/psychology/staff/martinlages/",
  speaker_name == "Anna Henschel" ~ "https://twitter.com/AnnaHenschel",
  speaker_name == "Anne Scheel" ~ "https://twitter.com/annemscheel",
  speaker_name == "Guillaume Rousselet" ~ "https://twitter.com/robustgar",
  speaker_name == "Zoltan Dienes" ~ "http://www.lifesci.sussex.ac.uk/home/Zoltan_Dienes/",
  speaker_name == "Ruud Hortensius" ~ "https://twitter.com/RuudHortensius",
  speaker_name == "Andrew Burns" ~ "https://www.gla.ac.uk/schools/socialpolitical/research/students/andrewburns/",
  speaker_name == "Lisa Kidd" ~ "https://www.gla.ac.uk/schools/medicine/staff/lisakidd/",
  speaker_name == "Georgi Karadzhov" ~ "https://twitter.com/g_karadzhov",
  speaker_name == "Alba Contreras Cuevas" ~ "https://es.linkedin.com/in/alba-contreras-cuevas-9a57a17b",
  speaker_name == "" ~ "",
  TRUE ~ speaker_url
)) %>%
  mutate(speaker_affiliation = case_when(
    speaker_name %in% glasgow_speakers ~ "University of Glasgow",
    TRUE ~ speaker_affiliation
    )) %>%
  mutate(Location = if_else(id %in% c(17054, 17080, 17102), "Zoom", Location))
```

```{r}
# fix timezone

jdf$end <- lubridate::ymd_hm(jdf$end, tz = "UTC") %>%
           lubridate::with_tz("Europe/London")

jdf$start <- lubridate::ymd_hm(jdf$start, tz = "UTC") %>%
           lubridate::with_tz("Europe/London")
```


<style>
  .abstract { padding-top: 1em; display: none; }
</style>

<br><br>
Methods & Metascience is a journal club and discussion group at the Institute of Neuroscience and Psychology at the University of Glasgow. Meetings are every other week on Wednesdays from 14:00 to 15:00 GMT on Zoom (ignore the auto-generated location for a few of the future events). Contact [Lisa](mailto://lisa.debruine@glasgow.ac.uk) for access to the zoom links. 

In addition to talks, we also run training events. If you would like to present or run a training workshop, please let [Lisa](mailto://lisa.debruine@glasgow.ac.uk) know!

This page is rendered when Lisa remembers, but is not dynamic. For a dynamically updated list of talks, please see [the events list](http://www.psy.gla.ac.uk/events/index.php?sub=12).


```{r}

sf <- lubridate::stamp("Sunday, Jan 17, 1999")
tm <- lubridate::stamp("15:34")

schedule <- jdf %>%
  mutate(Speaker = ifelse(speaker_url == "", speaker_name, paste0("[", speaker_name, "](", speaker_url,")"))) %>%
  mutate(Speaker = paste0(Speaker, "<br>", speaker_affiliation)) %>%
  mutate(abstract = ifelse(abstract == "", "", paste0(" <a>(abstract)</a><div class='abstract'>",abstract, "</div>"))) %>%
  mutate(Title = paste0(title, " ", resources, " ", abstract)) %>%
  #separate(start, c("Date", "start"), sep = "T") %>%
  #separate(end, c("x", "end"), sep = "T") %>%
  mutate(`Date/Time` = paste0(sf(start), "<br>", tm(start), "-", tm(end))) %>%
  mutate(Location = gsub("62 Hillhead Street, ", "", Location)) %>%
  select(Speaker, Title, `Date/Time`, Location, start) 

future <- filter(schedule, start >= Sys.Date()) %>%
  arrange(start) %>%
  select(-start)

past <- filter(schedule, start < Sys.Date()) %>%
  arrange(rev(start)) %>%
  select(-start)

```

```{r, results="asis"}
if (nrow(future) > 0L) {
  cat("\n### Upcoming Events\n\n")
  
  kable(future, escape = FALSE) %>%
    kable_styling("striped", fixed_thead = TRUE) %>%
    column_spec(1, width = "20%") %>%
    column_spec(2, width = "50%") %>%
    column_spec(3, width = "15%") %>%
    column_spec(4, width = "15%")
} else {
  cat("\n")
}
```

### Past Events

```{r}
kable(past %>% arrange(desc(`Date/Time`)), escape = FALSE) %>%
  kable_styling("striped", fixed_thead = TRUE) %>%
  column_spec(1, width = "20%") %>%
  column_spec(2, width = "50%") %>%
  column_spec(3, width = "15%") %>%
  column_spec(4, width = "15%")
```

<script>
  /* set up abstract toggling */
  $(document).ready(function () {
    $("a:contains(abstract)").click(function(e) {
      $(this).next().toggle();
      return false;
    });
  });
</script>

