---
title: ""
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```

<br><br>
Methodology & Metascience is a working group at the Institute of Neuroscience and Psychology at the University of Glasgow. You can find our schedule and materials at this website (which will be updated to a fancier blogdown site soon).

Our regular meetings will be Wednesday afternoons from 2pm-3pm in 605 (aka Meeting room) or 529/551 at 62 Hillhead St (aka "Seminar" room) or Room 520 (Computer Lab) in the Boyd Orr. In addition to talks, we will also be running some training events that we planned in our spring brainstorming meeting. If you would like to present or run a training workshop, please let [Dale](mailto://dale.barr@glasgow.ac.uk) know!

This site is still under construction; for an up to date list of talks, please see [the events list](http://www.psy.gla.ac.uk/events/index.php?sub=12).

### Schedule

```{r, results='asis'}

rss <- readLines("https://samoa.dcs.gla.ac.uk/events/rest/Feed/rss/141")

schedule <- tibble::tribble(
  ~Date, ~Speaker, ~speaker_link, ~Title, ~Time, ~Room,
  "2018-10-03", "Christoph Schild", "https://twitter.com/schildchristoph", 
    "Introduction to the [formr](https://formr.org/) survey framework in R [(slides)](https://osf.io/gu23h/)", 
    "15:00-16:00", "Seminar Room 529/551",

  "2018-10-10", "Dale Barr", "https://twitter.com/dalejbarr", 
    "Mixed-effects modeling of temporal autocorrelation: Keep it minimal",
    "14:00-15:00", "Meeting Room 605",

  "2018-10-24", "Ben Jones", "https://twitter.com/Ben_C_J",
    "Writing Registered Reports [(slides)](slides/2018_10_24_Ben_Jones.pdf)",
    "14:00-15:00", "Seminar Room 529/551",

  "2018-10-31", "Lisa DeBruine", "https://twitter.com/lisadebruine",
    "Your First Shiny App [(tutorial)](https://debruine.github.io/shiny-tutorials/)",
    "14:00-15:00", "Boyd Orr Computer Lab Room 520",

  "2018-11-07", "Jessica Flake", "https://www.jessicakayflake.com/", 
    "The Fundamental Role of Construct Validity in Original and Replicated Research",
    "14:00-15:30", "Seminar Room 529/551",

    "2018-11-14", "Martin Lages", "https://www.gla.ac.uk/schools/psychology/staff/martinlages/#/",
    "TBC",
    "14:00-15:00", "Meeting Room 605",

  "2018-11-21", "Robin Ince", "http://www.robinince.net/", 
    "Correcting for Multiple Comparisons",
    "14:00-15:00", "Meeting Room 605",
  
  
  "2018-11-28", "Larry Barsalou", "http://barsaloulab.org/",
    "The Situated Assessment Method (SAM^2): A new approach to measuring, understanding, and predicting health behaviours",
    "14:00-15:00", "Meeting Room 605",
  
  "2018-12-05", "Jack Taylor", "https://github.com/Jack-Tay",
    "The [LexOPS](https://github.com/Jack-Tay/LexOPS) Word Generator: A Web App for Stimulus Generation in Psycholinguistics",
    "14:00-15:00", "Meeting Room 605",
  
  "2018-12-12", "Dale Barr", "https://github.com/dalejbarr",
    "The exams package",
    "13:00-14:00", "Meeting Room 605"
)

schedule %>%
  mutate(Speaker = paste0("[", Speaker, "](", speaker_link,")")) %>%
  select(-speaker_link) %>%
  knitr::kable()

```

